%% Based on https://github.com/anishathalye/simple-resume-cv
\documentclass[letterpaper,11pt]{article}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage{graphicx}
\usepackage{tabularx}
\usepackage{multicol}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\fancyfoot{}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

% Sections formatting
\titleformat{\section}{\large\bfseries}{}{0em}{}
\titlespacing{\section}{0pt}{6pt}{2pt}

% Custom commands
\newcommand{\resumeItem}[1]{\item{\small{#1}}}
\newcommand{\resumeSubheading}[4]{
  \vspace{1pt}\textbf{#1} \hfill #2\\
  {\emph{#3}} \hfill {\small #4}\\
}
\newcommand{\resumeSubItem}[2]{\resumeItem{\textbf{#1}{: #2}}}
\newcommand{\resumeSubSection}[2]{\item\textbf{#1} --- #2}

% Document
\begin{document}

%==================== HEADER ====================
\begin{center}
    {\LARGE \scshape Cesar Alan Torres} \\ 
    \vspace{1pt}
    Tijuana, B.C., Mexico $\cdot$ \href{mailto:catq2596@gmail.com}{catq2596@gmail.com} $\cdot$ \href{https://cesartorres.org}{cesartorres.org} \\
\end{center}

%==================== ABOUT ====================
\section*{About Me}
Machine Learning and AI Researcher with an academic background in Soft Computing and Computer Vision. Passionate about Linux, self-hosting, and implementing SOTA models tailored to edge devices.

%==================== EXPERIENCE ====================
\section*{Experience}
\resumeSubheading{Thermo Fisher Scientific}{Nov 2024 -- Present}{Software Developer II — Tijuana, MX}{}
\begin{itemize}[leftmargin=0.15in, itemsep=2pt, topsep=2pt, parsep=0pt]
  \item Designed and developed GeneAI.
  \item Integrated LLMs including GPT, Claude, and various open-source LLMs within a secure, private deployment environment.
  \item Built internal infrastructure for managing embeddings, routing logic, and response generation.
  \item Enabled dynamic AI agent creation to support organization-wide automation and task handling.
  \item Contributed to a fully customizable, ChatGPT-style interface with complete control over UX and model governance.
\end{itemize}

\resumeSubheading{Samsung Research Tijuana}{Feb 2023 -- Nov 2024}{Machine Learning Engineer — Tijuana, MX}{}
\begin{itemize}[leftmargin=0.15in, itemsep=2pt, topsep=2pt, parsep=0pt]
  \item Adapted SOTA models to develop proof-of-concept systems.
  \item Built internal tools for data annotation and analysis.
  \item Implemented real-time CV models (Face Recognition, Action Recognition).
  \item Deployed LLMs/VLMs optimized for edge devices.
\end{itemize}

\resumeSubheading{Sistemas Audiovisuales Tijuana}{Jul 2011 -- Jan 2021}{Audio and Illumination Technician — Tijuana, MX}{}
\begin{itemize}[leftmargin=0.15in, itemsep=2pt, topsep=2pt, parsep=0pt]
  \item Operated and maintained audio, video, and lighting systems for a wide range of live events and conferences.
  \item Handled stage setup, technical logistics, and on-site troubleshooting to ensure smooth event execution.
  \item Oversaw end-to-end event production, including equipment configuration and coordination with performers or speakers.
  \item Contributed across multiple roles as part of a family-run business, including client communication, planning, and general operations.
\end{itemize}


%==================== EDUCATION ====================
\section*{Education}
\begin{tabularx}{\textwidth}{@{}Xr@{}}
\textbf{ScD. in Computer Science} & 2024 -- 2028 \\
\textit{Instituto Tecnológico de Tijuana} & \\
Focus: Generative AI, LLMs, Multimodal Learning & \\
\\[-1ex]
\textbf{MSc. in Computer Science} & 2021 -- 2023 \\
\textit{Instituto Tecnológico de Tijuana} & \\
Thesis: Deep Fuzzy Neural Learning Models & \\
\\[-1ex]
\textbf{BSc. in Computer Science Engineering} & 2015 -- 2019 \\
\textit{Cetys Universidad Tijuana} & \\
Cum Laude, Specialization in Computer Vision & \\
\end{tabularx}

%==================== SKILLS ====================
\section*{Skills}
\begin{itemize}[leftmargin=0.15in, itemsep=2pt]
  \item \textbf{Programming:} Python, C++, C, Java, JavaScript, MATLAB
  \item \textbf{ML Frameworks:} PyTorch, TensorFlow, Scikit-learn, Keras
  \item \textbf{Data Science:} NumPy, Pandas, SciPy, XGBoost, Matplotlib
  \item \textbf{Web:} HTML, CSS, React, Angular
  \item \textbf{Tools:} Git, Docker, Hugging Face, RoboFlow, Jira
  \item \textbf{Operating Systems:} Linux (Debian, Ubuntu, Arch), Windows, macOS
  \item \textbf{Cloud:} AWS (EC2, Lambda, S3), GCP (Compute Engine, SQL DBs)
  \item \textbf{Self-Hosting Services:} Pi-hole, NextCloud, Game Servers, Samba, Nginx, Wireguard
\end{itemize}

%==================== LANGUAGES ====================
\section*{Languages}
Spanish (Native), English (Advanced C1), German (Basic)

%==================== AWARDS ====================
\section*{Awards}
\begin{itemize}[leftmargin=0.15in]
  \resumeItem{1st Place: AI Hackathon by AiLabSchool, 2022 (Microsoft-sponsored)}
  \resumeItem{127th Place: IBM Behind the Code Marathon, 2020 (50,000+ participants)}
  \resumeItem{Outstanding Project: Engineering Project Fair, Cetys Universidad, 2019}
\end{itemize}

%==================== Publications ====================
\section*{Selected Publications}
\begin{itemize}[leftmargin=0.15in]
  \item Fuzzy Edge Detection as a Preprocessing Layer in Deep Neural Networks for Guitar Classification. \textit{Sensors}, 2022. \href{https://doi.org/10.3390/s22155892}{doi:10.3390/s22155892}
  \item Traffic Sign Recognition Using Fuzzy Preprocessing and Deep Neural Networks. \textit{Springer SCI}, 2023. \href{https://doi.org/10.1007/978-3-031-28999-6_5}{doi:10.1007/978-3-031-28999-6\_5}
  \item Fuzzy CNN Model Applied to Classification Problems. \textit{J. of Intelligent \& Fuzzy Systems}, 2024. \href{http://doi.org/10.3233/JIFS-219369}{doi:10.3233/JIFS-219369}
  \item Type-2 Fuzzy Image Enhancement to Improve the Performance of Convolutional Neural Networks. \textit{ISCMI}, 2023. \href{http://doi.org/10.1109/ISCMI59957.2023.10458559}{doi:10.1109/ISCMI59957.2023.10458559}
  \item Torres, C., Gonzalez, C.I. (2025). \textit{Automated Insights: LLMs in Neurodegenerative Disease Research and Comparison}. In: Martínez-Villaseñor, L., et al. \textit{Advances in Computational Intelligence. MICAI 2024 International Workshops}. Lecture Notes in Computer Science, vol 15464. Springer, Cham. \href{https://doi.org/10.1007/978-3-031-83879-8_9}{doi:10.1007/978-3-031-83879-8\_9}
  \item Torres, C., Gonzalez, C.I., Garcia, M., \& Merelo-Guervos, J. (2025). \textit{Efficient Domain-Specific LLMs: Energy Profiling in Medical QA Tasks}. Accepted for presentation and publication at IJCNN 2025, Rome, Italy.
\end{itemize}

%==================== Presentations ====================
\section*{Selected Presentations}
\begin{itemize}[leftmargin=0.15in]
  \item Deep Neural Network Approach for Guitar Type Classification in Real Time. VII Congreso Internacional de Investigación, UABC, Apr 2022.
  \item Fuzzy Convolutional Layer in Deep Neural Networks for Feature Extraction. ISCI 2022, TecNM, Aug 2022.
  \item Type-2 Fuzzy Image Enhancement to Improve the Performance of Convolutional Neural Networks. ISCMI 2023, CDMX.
  \item Fuzzy Convolutional Neural Network Model Applied to Classification Problems. CCAIS 2023.
  \item LLMs Oriented to Neurodegenerative Research. ISCI 2024, TecNM.
  \item Type-2 Fuzzy Deep Learning Approach Applied to Classify Alzheimer's Disease. IPN-CITEDI, AI and Quantum Computing Seminar 2024.
  \item Automated Insights: LLMs in Neurodegenerative Disease Research and Comparison. MICAI 2024, SMIA Workshop.
\end{itemize}

\end{document}